Predicting Covid Data

### 2022-12-06 main.rmd
Adjusted introduction and formatted the plots

* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function:  
$a+b*erf(c*x-d)$.
* Used the function to approximate the number of cumulative positive cases in Italy
* Performed a 150 Monte Carlo simulations to predict the day in which the peak of the number of daily cases in Italy occurs.
* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2) +
  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]), color="blue")
```

>>>>

* The time evolution of he number of cumulative diagnosed positive cases and fatalities in China approximates the distribution of a gauss error function: $a+b*erf(c*x-d)$.
* Performed the function on Italy data to approximate the number of cases.
* Performed 150 Monte Carlo simulations to predict the day in which the peak of the number of daily cases in Italy occurs.

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) +
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```
